Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity

### 2017-06-01 manuscript.Rmd
add info about low number of records for rare phyla

There are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups are well represented in museum collections, the small organisms of the meiofauna are virtually absent: 12 of the 25 phyla represented in the dataset have less than 500 specimens in museums.

>>>>

There are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups represent the bulk of the records for marine invertebrates in museum collections, the small organisms of the meiofauna are virtually absent. Of the `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` are represented by less than 500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the total number of records.
